\section{Fuentes de información}\label{fuentes-de-informacion}

En el presente trabajo se han usado múltiples fuentes de información, dependiendo del área monetaria y de la magnitud correspondiente.

A continuación se expone a modo de resumen una lista de las fuentes de datos consultadas y utilizadas por área monetaria:

Estados Unidos:
\begin{itemize}
  \item Gasto agregado: Reserva Federal. \textit{Gross Domestic Product, Quarterly, Billions of Dollars}. \url{https://fred.stlouisfed.org/series/GDP}.
  \item Oferta monetaria: M3 de ShadowStats. \url{http://www.shadowstats.com}.
  \item Inflación: Reserva Federal. \textit{Consumer Price Index for All Urban Consumers: All Items in U.S. City Average. Seasonally adjusted} (CPIAUCSL). \url{https://fred.stlouisfed.org/series/CPIAUCSL}.
\end{itemize}

Eurozona (datos del BCE):
\begin{itemize}
  \item Gasto agregado: dos opciones:
        \begin{itemize}
          \item \textit{Gross domestic product at market prices, Euro area 20 (fixed composition) as of 1 January 2023, Quarterly}. \url{https://data.ecb.europa.eu/data/datasets/MNA/MNA.Q.Y.I9.W2.S1.S1.B.B1GQ._Z._Z._Z.EUR.LR.N}.
          \item Utilizado: \textit{Gross domestic product at market prices, Euro area (Member States and Institutions of the Euro Area) changing composition, Quarterly}. \url{https://data.ecb.europa.eu/data/datasets/MNA/MNA.Q.N.U2.W2.S1.S1.B.B1GQ._Z._Z._Z.EUR.V.N}.
        \end{itemize}
  \item Oferta monetaria: \textit{Monetary aggregate M3 reported by MFIs, central gov. and post office giro institutions in the euro area (stocks), Euro area (changing composition), Monthly}. \url{https://data.ecb.europa.eu/data/datasets/BSI/BSI.M.U2.N.V.M30.X.1.U2.2300.Z01.E}.
  \item Inflación: HICP: \textit{HICP - Overall index, Euro area (changing composition), Monthly}. \url{https://data.ecb.europa.eu/data/datasets/ICP/ICP.M.U2.N.000000.4.INX}
\end{itemize}

Suiza (datos del SNB):
\begin{itemize}
  \item Gasto agregado: \texttt{gdpap\{BBIPS\}}.
  \item Oferta monetaria: M3 \texttt{snbmonagg\{GM3\}}.
  \item Inflación: diferentes opciones
        \begin{itemize}
          \item Utilizada: \textit{SNB National index (Dec. 2020=100)}. \texttt{plkopr\{LD2010100\}}.
          \item \textit{Eurostat HICP - monthly data (index)}. \url{https://ec.europa.eu/eurostat/databrowser/view/prc_hicp_midx/default/table?lang=en&category=prc.prc_hicp}
          \item \textit{IMF PCPIP: Inflation rate, averge consumer prices}. \url{https://data.imf.org/?sk=4ffb52b2-3653-409a-b471-d47b46d904b5}
        \end{itemize}
\end{itemize}

Reino Unido:
\begin{itemize}
  \item Gasto agregado: ONS \textit{Gross Domestic Product at market prices: Current price: Seasonally adjusted £m, quarterly}. \url{https://www.ons.gov.uk/economy/grossdomesticproductgdp/timeseries/ybha/pn2}.
  \item Oferta monetaria: BoE M4x, \textit{LPMAUYN, Monthly amounts outstanding of M4 (monetary financial institutions' sterling M4 liabilities to private sector) (in sterling millions) seasonally adjusted}. \url{https://www.bankofengland.co.uk/boeapps/database/FromShowColumns.asp?Travel=NIxAZxI1x&FromCategoryList=Yes&NewMeaningId=LM4,LM4L&CategId=6&HighlightCatValueDisplay=M4}.
  \item Inflación: ONS \textit{CPI INDEX 00: ALL ITEMS 2015=100}. \url{https://www.ons.gov.uk/economy/inflationandpriceindices/timeseries/d7bt/mm23}.
\end{itemize}

Japón:
\begin{itemize}
  \item Gasto agregado: Reserva Federal \textit{Gross Domestic Product for Japan. Billions of Yen,
          Seasonally Adjusted. Quarterly}. \url{https://fred.stlouisfed.org/series/JPNNGDP}.
  \item Oferta monetaria: BoJ \textit{M3/Average Amounts Outstanding/Money Stock} (\texttt{MD02'MAM1NAM3M3MO}). \url{https://www.stat-search.boj.or.jp/ssi/mtshtml/md02_m_1_en.html}.
  \item Inflación: e-Stat \textit{2020-Base Consumer Price Index. Monthly Report. 2024Jul.}. \url{https://www.e-stat.go.jp/en/stat-search/files?page=1&layout=datalist&toukei=00200573&tstat=000001150147&cycle=1&year=20240&month=23070907&tclass1=000001150149&result_back=1&tclass2val=0}.

\end{itemize}